Supplemental Material for submission ``Do Objects in Real-World Images Have a Canonical Name?''

### 2019-05-21 papers/EMNLP2019/analysis_table_wModelpreds.tex
magic! small table, more space

			\begin{tabular}{p{4cm}|p{4cm}|p{4cm}|p{4cm}}

@@

				\multicolumn{4}{c}{\textbf{VG: sandwich}}\\

@@

				\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2386509_681763_supercat_unique.png}} hotdog (14), \underline{food} (7), bun (4), sandwich (3),  \underline{bread} (2) [banana (1)]\\ 

@@

				 & \textit{hotdog}, \textit{bun}, \textit{banana}, \textit{bread}, table \\ 

@@

				\multicolumn{4}{c}{\textbf{VG: bridge} }\\ 

@@

				\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2412972_3494120_singleton_obj.png}} pier (6), railing (5), dock (5), bridge (5), fence (4), rail (3), boardwalk (3)\\

@@

				& \textit{railing}, water, \textit{pier}, ocean, \textit{fence}, deck, \textit{dock} \\ 

@@

				\multicolumn{4}{c}{\textbf{VG: bed}}\\ 

@@

				\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/498222_3135415_singleton_obj.png}} bed (12), sleeping bag (9), blanket (7), bed sheet (5)\\ 

@@

				& \textit{bed}, comforter, \textit{blanket}, cover, sheet \\ 
				\multicolumn{4}{c}{\textbf{VG: batter}}\\
				\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2372219_2683892_supercat_unique.png}} man (24), cap (5), \underline{person} (3), \underline{baseball player} (2) &
				\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2394377_464684_singleton_obj.png}} man (13), \underline{baseball player} (7), batter (5), \underline{player} (3), helmet (2) [player (1)]&
				\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2337552_957263_singleton_obj.png}} pants (6), \underline{player} (5), shoe (4), bat (4), \underline{person} (4), legs (4), \underline{baseball player} (3), hitter (2)\\ 
				\textit{man}, player, \textit{person}, shirt, guy
				& \textit{player}, \textit{batter}, \textit{man}, \textit{baseball player}, uniform

@@

				\multicolumn{4}{c}{\textbf{VG: robe}}\\
				\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/160_1058761_supercat_unique.png}} dress (30), uniform (2) &
				woman, outfit, dress, girl, suit
				& woman, outfit, \textit{dress}, girl, suit
				%, stuffed animals \\ 

@@

@@

>>>>

			\begin{tabular}{p{2.8cm}|p{2.8cm}|p{2.8cm}|p{2.8cm}|p{2.8cm}|p{2.8cm}}

@@

				\multicolumn{4}{c|}{\textbf{VG: sandwich}} & \multicolumn{2}{c}{\textbf{VG: robe}}\\

@@

				\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2386509_681763_supercat_unique.png}} hotdog (14), \underline{food} (7), bun (4), sandwich (3),  \underline{bread} (2) [banana (1)] &
				\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/160_1058761_supercat_unique.png}} dress (30), uniform (2)\\ 

@@

				 & \textit{hotdog}, \textit{bun}, \textit{banana}, \textit{bread}, table
				 & woman, outfit, dress, girl, suit
				& woman, outfit, \textit{dress}, girl, suit \\ 

@@

				\multicolumn{4}{c|}{\textbf{VG: bridge} } & \multicolumn{2}{c}{\textbf{VG: robe}}\\ 

@@

				\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2412972_3494120_singleton_obj.png}} pier (6), railing (5), dock (5), bridge (5), fence (4), rail (3), boardwalk (3) &

@@

				& \textit{railing}, water, \textit{pier}, ocean, \textit{fence}, deck, \textit{dock} 
\\ 

@@

				\multicolumn{4}{c|}{\textbf{VG: bed}} & \multicolumn{2}{c}{\textbf{VG: batter}}\\ 

@@

				\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/498222_3135415_singleton_obj.png}} bed (12), sleeping bag (9), blanket (7), bed sheet (5) &
				\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2337552_957263_singleton_obj.png}} pants (6), \underline{player} (5), shoe (4), bat (4), \underline{person} (4), legs (4), \underline{baseball player} (3), hitter (2)\\ \\ 

@@

				& \textit{bed}, comforter, \textit{blanket}, cover, sheet 

@@

%				\multicolumn{4}{c}{\textbf{VG: batter}}\\
%				\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2372219_2683892_supercat_unique.png}} man (24), cap (5), \underline{person} (3), \underline{baseball player} (2) &
%				\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2394377_464684_singleton_obj.png}} man (13), \underline{baseball player} (7), batter (5), \underline{player} (3), helmet (2) [player (1)]&
%				\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2398907_2901496_singleton_obj.png}}  boy (7), helmet (5), \underline{baseball player} (4), \underline{player} (4), man (3), child (3), batter (3), dress (2), kid (2)&
%				\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2337552_957263_singleton_obj.png}} pants (6), \underline{player} (5), shoe (4), bat (4), \underline{person} (4), legs (4), \underline{baseball player} (3), hitter (2)\\ 
%				%
%				\rowcolor{lightgray}
%				\textit{man}, player, \textit{person}, shirt, guy
%				& \textit{player}, \textit{batter}, \textit{man}, \textit{baseball player}, uniform
%				& \textit{boy}, \textit{player}, \textit{batter}, \textit{kid}, girl, \textit{child}, \textit{baseball player}, person, uniform
%				& \textit{player}, batter, \textit{person}, man, uniform, boy, \textit{baseball player}, dirt \\ 

@@

%				\multicolumn{4}{c}{\textbf{VG: robe}}\\
%				\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2373180_2333161_singleton_obj.png}} robe (27), \underline{bathrobe} (5) &
%				\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/160_1058761_supercat_unique.png}} dress (30), uniform (2) &
%				\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2334612_2838713_supercat_unique.png}}  robe (11), jacket (7), clothes (6), bag (3), dress (2), man (2) &
%				\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2340041_2137546_supercat_ambiguous.png}} jacket (10), \underline{sweater} (9), coat (3), doll (3), toy (3), \underline{shirt} (2), bear (2), robe (2) [stuffed animal (1)]\\ 
%				%
%				\rowcolor{lightgray}
%				woman, outfit, dress, girl, suit
%				& woman, outfit, \textit{dress}, girl, suit
%				& \textit{man}, shirt, person, \textit{robe}, coat, \textit{jacket}%, woman, outfit, clothes, clothing
%				& teddy bear, \textit{bear}, dog, \textit{toy}, \textit{stuffed animal}, blanket, toys
%				%, stuffed animals \\ 
%				%
%				% 				

@@

\begin{table*}
	\centering
	\small
	\begin{tabular}{l@{~}|@{~}r@{~}r@{~}rr@{~}|@{~}r@{~}r@{~}rr@{~}|@{~}r@{~}r@{~}rr}
		\toprule
		%{} &  All images-top=VG &  All images-top=MN &  All images-top\$\textbackslash in\$MN &  All images-KL &  VGnotMN-top=VG &  VGnotMN-top=MN &  VGnotMN-top\$\textbackslash in\$MN &  VGnotMN-KL &  notTrain-top=VG &  notTrain-top=MN &  notTrain-top\$\textbackslash in\$MN &  notTrain-KL \\
		& \multicolumn{12}{c}{Image subset} \\
		&	\multicolumn{4}{c}{All ($24,585$)} 
		& \multicolumn{4}{c}{VG$\neq$MN ($6,280$)}
		& \multicolumn{4}{c}{$\neg$Training ($2,281$)} \\
		\midrule
		&  \multicolumn{2}{c}{single-label}
		&  \multicolumn{2}{c}{multi-label}
		&  \multicolumn{2}{c}{single-label}
		&  \multicolumn{2}{c}{multi-label}
		&  \multicolumn{2}{c}{single-label}
		&  \multicolumn{2}{c}{multi-label} \\
		Domain	 &  =VG & =MN & $\in$MN  &  KL
		&  =VG & =MN & $\in$MN  & KL
		&  =VG & =MN & $\in$MN  & KL\\ 
		\midrule \vspace{.6ex}
		all            &               68.7 &                 76.8 &                   94.8 &            0.9 &            20.7 &              52.6 &                92.4 &         1.2 &             63.5 &               73.1 &                 92.5 &          1.0 \\ 
		home           &               70.0 &                 74.7 &                   93.4 &            1.1 &            24.3 &              47.5 &                91.4 &         1.4 &             67.2 &               70.5 &                 92.5 &          1.2 \\
		food           &               60.0 &                 71.9 &                   87.7 &            1.0 &            14.2 &              48.9 &                76.6 &         1.5 &             46.6 &               62.1 &                 80.1 &          1.3 \\
		buildings      &               57.5 &                 70.7 &                   92.1 &            1.3 &             7.9 &              63.4 &                89.8 &         1.5 &             44.3 &               60.2 &                 88.6 &          1.4 \\
		vehicles       &               69.8 &                 72.8 &                   97.6 &            0.6 &            35.3 &              46.1 &                97.4 &         0.7 &             67.2 &               73.5 &                 96.4 &          0.7 \\
		animals/plants &               92.7 &                 94.8 &                   97.7 &            0.4 &            20.3 &              65.0 &                94.0 &         0.9 &             91.3 &               92.6 &                 96.2 &          0.5 \\
		clothing       &               63.3 &                 70.9 &                   92.6 &            1.0 &            19.9 &              48.5 &                90.3 &         1.2 &             50.8 &               60.2 &                 87.4 &          1.3 \\
		people         &               48.5 &                 70.7 &                   95.5 &            1.2 &            13.8 &              58.9 &                95.3 &         1.3 &             42.2 &               68.2 &                 92.8 &          1.2 \\
		\bottomrule
		%Baseline      &                3.3 &                  5.2 &                   12.0 &            -- &             1.7 &               9.3 &                21.8 &         -- &              3.0 &                5.0 &                 11.9 &          -- \\
		Baseline       &                3.9 &                  4.6 &                    5.6 &            -- &             0.1 &               3.0 &                 3.8 &         -- &              3.8 &                4.6 &                  5.8 &          -- \\
	\end{tabular}
	\caption{Baseline: The most frequent name. Random baseline (KL with random distributions) for each image set: 6.9 (all), 6.5 (VG$\neq$MN) and 6.9 ($\neg$Training). The numbers in parentheses give the \# instances in each set.	\label{tab:model}}
\end{table*}

### 2019-05-21 papers/EMNLP2019/modeling.tex
magic! small table, more space

\begin{table*}
	\centering
	\small
	\begin{tabular}{l@{~}|@{~}r@{~}r@{~}rr@{~}|@{~}r@{~}r@{~}rr@{~}|@{~}r@{~}r@{~}rr}
		\toprule
		%{} &  All images-top=VG &  All images-top=MN &  All images-top\$\textbackslash in\$MN &  All images-KL &  VGnotMN-top=VG &  VGnotMN-top=MN &  VGnotMN-top\$\textbackslash in\$MN &  VGnotMN-KL &  notTrain-top=VG &  notTrain-top=MN &  notTrain-top\$\textbackslash in\$MN &  notTrain-KL \\
		& \multicolumn{12}{c}{Image subset} \\
		&	\multicolumn{4}{c}{All ($24,585$)} 
		& \multicolumn{4}{c}{VG$\neq$MN ($6,280$)}
		& \multicolumn{4}{c}{$\neg$Training ($2,281$)} \\
		\midrule
		&  \multicolumn{2}{c}{single-label}
		&  \multicolumn{2}{c}{multi-label}
		&  \multicolumn{2}{c}{single-label}
		&  \multicolumn{2}{c}{multi-label}
		&  \multicolumn{2}{c}{single-label}
		&  \multicolumn{2}{c}{multi-label} \\
		Domain	 &  =VG & =MN & $\in$MN  &  KL
		&  =VG & =MN & $\in$MN  & KL
		&  =VG & =MN & $\in$MN  & KL\\ 
		\midrule \vspace{.6ex}
		all            &               68.7 &                 76.8 &                   94.8 &            0.9 &            20.7 &              52.6 &                92.4 &         1.2 &             63.5 &               73.1 &                 92.5 &          1.0 \\ 
		home           &               70.0 &                 74.7 &                   93.4 &            1.1 &            24.3 &              47.5 &                91.4 &         1.4 &             67.2 &               70.5 &                 92.5 &          1.2 \\
		food           &               60.0 &                 71.9 &                   87.7 &            1.0 &            14.2 &              48.9 &                76.6 &         1.5 &             46.6 &               62.1 &                 80.1 &          1.3 \\
		buildings      &               57.5 &                 70.7 &                   92.1 &            1.3 &             7.9 &              63.4 &                89.8 &         1.5 &             44.3 &               60.2 &                 88.6 &          1.4 \\
		vehicles       &               69.8 &                 72.8 &                   97.6 &            0.6 &            35.3 &              46.1 &                97.4 &         0.7 &             67.2 &               73.5 &                 96.4 &          0.7 \\
		animals/plants &               92.7 &                 94.8 &                   97.7 &            0.4 &            20.3 &              65.0 &                94.0 &         0.9 &             91.3 &               92.6 &                 96.2 &          0.5 \\
		clothing       &               63.3 &                 70.9 &                   92.6 &            1.0 &            19.9 &              48.5 &                90.3 &         1.2 &             50.8 &               60.2 &                 87.4 &          1.3 \\
		people         &               48.5 &                 70.7 &                   95.5 &            1.2 &            13.8 &              58.9 &                95.3 &         1.3 &             42.2 &               68.2 &                 92.8 &          1.2 \\
		\bottomrule
		%Baseline      &                3.3 &                  5.2 &                   12.0 &            -- &             1.7 &               9.3 &                21.8 &         -- &              3.0 &                5.0 &                 11.9 &          -- \\
		Baseline       &                3.9 &                  4.6 &                    5.6 &            -- &             0.1 &               3.0 &                 3.8 &         -- &              3.8 &                4.6 &                  5.8 &          -- \\
	\end{tabular}
	\caption{Baseline: The most frequent name. Random baseline (KL with random distributions) for each image set: 6.9 (all), 6.5 (VG$\neq$MN) and 6.9 ($\neg$Training). The numbers in parentheses give the \# instances in each set.	\label{tab:model}}
\end{table*}
%
% mismatch between the visual awareness of the target object (man) and that of the competitor object (shirt)

@@

Model effectiveness is assessed in two settings, the commonly used single-label setting and a multi-label setting. 
In the former, for each instance, we compare the model's top prediction (the object label with the highest score in\ $S$) to its VG name and to the top response in MN, respectively, and report the average accuracy across all instances (\textit{=VG} and \textit{=MN}, respectively).
In the multi-label setting, we report the average accuracy of the top prediction matching any of the responses in MN.
We also test the model's ability to mimick the distribution of names provided by humans, by treating $S$ as a probability distribution and comparing it to the probability distribution~$M$ over the MN responses (estimated by normalizing the name counts; as in the analysis above, we remove names with frequency 1 to account for possible noise\gbt{@Carina, pls revise}). 
We report the average Kullback-Leibler divergence~$\mathrm{D_{KL}}(M||S)$ \cite{kullback1951information}.
We compare Bottom-up against a random baseline for the KL divergence, and against a most-frequent name baseline \cs{not sure whether the latter, at least in its current form, makes sense. TBD?}.
\gbt{Random baseline values missing; I'm not sure if it makes sense; we could maybe compare it to the single-label distribution: Compare $S$ to $M$, like we do, and then to a distribution to vectors with 1, 0, 0, 0... with MN top. Not sure if this is too ``cheap'' -- is it a matter of course that it will be lower? Not if the distribution doesn't reflect the actual $M$?}

>>>>

%
% mismatch between the visual awareness of the target object (man) and that of the competitor object (shirt)

@@

Model effectiveness is assessed in two settings, the commonly used single-label setting and a multi-label setting. 
In the former, for each instance, we compare the model's top prediction (the object label with the highest score in\ $S$) to its VG name and to the top response in MN, respectively, and report the average accuracy across all instances (\textit{=VG} and \textit{=MN}, respectively).
In the multi-label setting, we report the average accuracy of the top prediction matching any of the responses in MN.
We also test the model's ability to mimick the distribution of names provided by humans, by treating $S$ as a probability distribution and comparing it to the probability distribution~$M$ over the MN responses (estimated by normalizing the name counts; as in the analysis above, we remove names with frequency 1 to account for possible noise\gbt{@Carina, pls revise}). 
We report the average Kullback-Leibler divergence~$\mathrm{D_{KL}}(M||S)$ \cite{kullback1951information}.
We compare Bottom-up against a random baseline for the KL divergence, and against a most-frequent name baseline \cs{not sure whether the latter, at least in its current form, makes sense. TBD? MF name baseline: I would say it's not relevant for this paper (we mainly compare different settings).}.
\gbt{Random baseline values missing; I'm not sure if it makes sense; we could maybe compare it to the single-label distribution: Compare $S$ to $M$, like we do, and then to a distribution to vectors with 1, 0, 0, 0... with MN top. Not sure if this is too ``cheap'' -- is it a matter of course that it will be lower? Not if the distribution doesn't reflect the actual $M$?}
